\section{Humans}\label{sec:human}
Your standard garden variety person.
Comes in all sorts of shapes, sizes and colours.
Generally lazy, yet territorial.

Human kingdoms cover most of Saoghaal's coastal areas, thinning out into smaller settlements towards the more inhospitable areas of the region.

\paragraph{Physical Description}
Humans are bipedal creatures that come in a wide variety of shapes and sizes.
Adult humans typically have sizes ranging from between around 1.5m to around 2.1m.
Skin and hair colour varies by region of origin, but typically ranges from various shades of tan to dark brown.

\paragraph{Society}
Humans have the widest variety of societal structures of any races in Saoghaal.
Ranging from feudalist empires, to elective monarchies, to democracies, there is almost no limit to the kinds of societal structure present within Saoghaal.

\paragraph{Relations}
The expansionist and territorial nature of humans means they've interacted with most---if not all---other races at some point in their history.
Whether it be through war, exploration, diplomacy, or slavery; humans have managed to make a name for themselves in every corner of the world.

\paragraph{View on the Undead}
The humans' view on the undead is about as varied as their cultures.
Some view the Curse's ability to bring people back to life as just another aspect of life, while others outright condemn it.

\paragraph{Religion}
Humans will worship pretty much everything, and they are very tribalist about it.
Regardless of being the same species or nationality, even a difference in religion will be enough to cause conflict amongst humans.

\paragraph{Adventurers}
As humans come from varied cultures and backgrounds, they also have many varied reasons for becoming adventurers.
Likewise, humans will have a myriad reasons to join just about any available spot in an adventuring party.

\paragraph{Names}
The naming of individuals varies widely from culture to culture, see Section~\ref{sec:saoghaal} for names common in the various regions.

\subsection{Racial Traits}
\paragraph{Versatile, Yet Reckless}
The human versatility comes at the cost of perhaps not making the wisest decisions.
Humans get a $Wis -1$ modifier on character creation.

\paragraph{Surprisingly Tough}
Turns out, humans are surprisingly hard to kill all things considered.
Their toughness rewards them with a $Con+1$ bonus on character creation.

\paragraph{Divisive to a Fault}
Humans are---by their very nature---divisive individuals.
Where some races may have prejudices against certain groups or races, humans instead do this on an individual basis---even against other humans.
Certain cultures tend to skew this prejudice in certain directions, but ultimately the individuals decide for themselves.