\section{Sirens -- Winged Vocal Charmers}
Ancient race of creatures known for their beautiful enchanting songs, said to be the progenitors of bardic magic.
Legend has it that sirens used to be regular humans that once got cursed by an evil sorceror eons ago, dooming them to walk the earth as bird-people.

\paragraph{Physical Description}
Sirens are characterised by their humanoid shape, feathreed bodies, bird-like feet, wings, and short stature, rarely growing taller than 1.6m.
The expected lifespan of a siren is around 65 years.
Sirens are flightless birds, however do have the ability to glide for long distances.
Longest recorded Siren glide, was 1.2km.

Sirens come in a wide variety of colours, ranging from muted blues to deep reds to blacks and browns.
Their colour and feather patterns generally depend on the region and sub-species of Siren, generally favouring blues near the sea, and browns or reds further inland.

No male Sirens are known to exist anywhere in the world, as such Sirens typically have to seek mates of other compatible species, which include Humans, Trolds, and Jotun.

\paragraph{Society}
Sirens are often found near large bodies of water, typically at sea, where they will live most of their lives.
Their song has been said to cause shipwrecks, although no solid evidence towards this has ever been provided.
Sirens are generally known to be mild-mannered and meek.

Sirens typically live in small villages, but have been known to live in the larger human seaside settlements such as \textit{Sparr} and \textit{Chapman's Haven}.
Sirens don't normally wear clothes unless surrounded by humans or other clothes-wearing peoples, but to them wearing clothes is more a sign of solidarity and respect for the people they live among, moreso than out of necessity.

\paragraph{Relations}
Historically, the relationship between Sirens and Humans has been a bit on the sour side, due to the rumours of Sirens kidnapping sailors at sea.
However, while there is no open conflict between the species, there is 

\paragraph{View on the Undead}

\paragraph{Religion}

\paragraph{Adventurers}

\paragraph{Names}

\subsection{Racial Traits}