\section{Metaphysics}
\subsection{Shades}
Shades are the souls of people as they exist within Niflhel.
\subsection{Husks}
Husks are the living bodies of people who have lost their souls.
\subsection{Soul Sickness}
Shades are capable of possessing any available body they want, but might risk contracting Soul Sickness if not aided by a ritual.
The ritual's purpose is to relieve the maddening pain caused by entering a foreign body.
If the person's will isn't strong enough to withstand this pain, their mind risks cracking.
The Soul Sickness gets worse with each successive takeover.

People inflicted with Soul Sickness often show signs of paranoia and have nervous ticks.
\subsubsection{Frenzy}
The pain of successive possessions is enough to break the minds of even the strongest of Shades.
After a while, the Shade loses all sense of self and becomes \textit{addicted} to dying.
At this state, the Shade is ``Frenzied'' and will possess anything and everything it can get its hands on, including the husks of animals and rotting corpses.

The only way to get rid of a Frenzied Shade for good, is by killing it in Niflhel.
\subsection{Niflhel -- The Underworld}
Niflhel is a twisted, incomplete, and broken depiction of the material plane.
It is a patchwork of how its inhabitants remembered the material plane.
It roughly coinsides with \textit{reality}, but due to its many inhabitants, the combined memory contains discrepensies.

Niflhel is in part inhabited by the spirits of creatures who died in the material plane, and in part by predatory creatures native to the land.
The spirits go by many names, but are commonly referred to as \textit{Shades} (See Section~\ref{sec:shade}).

Due to Niflhel's nature, the land isn't divided into countries per se, although small organised settlements of people do exist within this realm.