\subsection{The Venzig Alliance -- The Country Without Borders}
\begin{tabular}{r | l}
    \textbf{Capital City} & Chapman's Haven\\
    \textbf{Total Population} & ca. 1'257'380\\
    \textbf{National Language} & Venzig Creole
\end{tabular}

The Venzig Allience is a large seafaring nation often referred to as ``The Country Without Borders'' by the denizens of the Saoghaal region due to its rather unusual geography.
Unlike most nations, the Venzig Alliance isn't a state at all, nor is it bound by geography.
It almost entirely consists of various merchants guilds from across the world, which democratically cooperate amongst each other.

\subsubsection{Geography}
The Venzig Alliance mainly exists as a loose collection of port towns spread out all over the Saoghaal region, primarily on key islands on the Saoghaalta Sea.
The Alliance is so distributed in fact, that it is possible to find small taverns in remote locations that bear the Alliance insignia; these taverns are considered Alliance territory, and operate---for all intents and purposes---as consulates, and will be defended as such if need be.
That being said, these consulates will obey local laws to stay on good terms with the host countries they reside in.
An official number of these consulates is currently unknown, but it is believed to be in the thousands.

The capital city---Chapman's Haven---is an old port town situated within what is now the \textit{Kalmic Confederacy}.
The founders of the Alliance is said to have been a group of business owners of a variety of shops and trading companies in the city who got tired of the corrupt local lord's neglegance and decided to take matters into their own hands.
They ended up outright buying the town, thus laying the groundworks for what later became the Venzig Alliance.

\subsubsection{Politics}
In a world of kingdoms, the Venzig Alliance is the only democracy within Saoghaal.
All major decision making is done by the Venzig Council, which consists of various people within respected leadership positions within the alliance---such as, shipping magnates, ship captains, guild leaders, tavern owners, and even farmers.
The criteria for becoming a council member is nebulous at best; though it typically involves petitioning by council members and Alliance denizens.

Being a council member is an unpaid position, as such most of the council members are usually too busy working their normal day-jobs to be physically present at the council chamber.
Because of this, most council decisions are decided via mail sent to the capital.
Small local councils also exist, and serve as smaller intermediate hubs for quicker decision making.
Things voted upon by the smaller councils is then later relayed to the main council in the capital.

\subsubsection{Language}
The Venzig Creole is made up of loanwords from around 12 different languages found around the Saoghaalta Sea with meanings and grammar drastically simpler than their root languages.
The language mainly serves as a lingua franca between all the nations touched by the Alliance, and is widely spoken within the Alliance itself.
Scholars across Saoghaal consider the language a \textit{creole} due to its widespread cross-generational use on the smaller islands across the Saoghaalta Sea.
Regional dialects of the creole have even been observed although, the uninitiated may find it difficult to distinguish them.